% Document source code gathered on:
% https://www.overleaf.com/latex/templates/faangpath-simple-template/npsfpdqnxmbc
% Original owner and attributions can be found there.
% directory must include resume.cls to compile (the class file)

% Issue 1 needs a file changed to kick off a runner
% TODO: store artifacts somewhere


\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Garett Loghry}
% You can merge both of these into a single line, if you do not have a website.
\address{+1(360) 931-2390 \\ Vancouver, WA}
\address{\href{https://github.com/gloghry}{github.com/gloghry} \\ \href{https://www.linkedin.com/in/gloghry/}{linkedin.com/in/gloghry/} \\ \href{https://gitlab.com/gloghry}{gitlab.com/gloghry}}
\address{\href{mailto:loghry.g@gmail.com}{loghry.g@gmail.com}}

\begin{document}
	%----------------------------------------------------------------------------------------
	%	SUMMARY
	%----------------------------------------------------------------------------------------
	\begin{rSection}{SUMMARY}
		I am a software engineer who has a background in embedded engineering and software development.
	\end{rSection}

	%----------------------------------------------------------------------------------------
	% 	TECHNICAL STRENGTHS	
	%----------------------------------------------------------------------------------------
	\begin{rSection}{TECHINICAL SKILLS}

		\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
			Programming Languages 	& C, C$^\sharp$, Python, Java, Bash, Rust, MATLAB, Kotlin. \\
		\end{tabular}

		\begin{tabular}{ @{} >{\bfseries} l @{\hspace{6ex}} l @{\hspace{6ex}} l}
			Experienced in	 	& Embedded Systems	& CAN Protocol, Git, SVN, System  Architecture. \\
						& Robotics 		& ROS2, NVIDIA Jetson, Raspberry Pi. \\
						& Machine Learning 	& NVIDIA Isaac Ecosystem, PyTorch, ONNX. \\
						& CI/CD 		& Jenkins, JFrog, GitHub Actions, Azure DevOps. \\
		\end{tabular}
	\end{rSection}

	%----------------------------------------------------------------------------------------
	%	WORK EXPERIENCE
	%----------------------------------------------------------------------------------------
	\begin{rSection}{EXPERIENCE}
		\textbf{Embedded Software Engineer} \hfill Aug 2024 - Present \\
		Hyster-Yale Materials Handling - \textit{Innovation Team} \hfill \textit{Clackamas, OR}
		\begin{itemize} \itemsep -5pt {}
			\item OAS
			\begin{itemize} \itemsep -5pt {}
				\item Wrote and maintained C code and MATLAB models related to Hyster-Yale's ``Operator Assist System'' (OAS). 
				\item You can see the work we do with OAS at \href{https://www.hyster.com/en-us/north-america/technology/telematics/hyster-reaction/}{Hyster Reaction} and \href{https://www.yale.com/en-us/north-america/technology/yale-reliant/}{Yale Reliant}.
				\item Contributed to technical documentation and production release processes to ensure product quality, a robust life-cycle, and ensure industry standards were met.
				\item Worked with cross-functional teams of other engineers, testers, and managers to shorten development times, enhance product knowledge, and reduce the ``bus factor''.
            \end{itemize}	
			\item Autonomous Ground Vehicle (AGV) Prototype
            \begin{itemize} \itemsep -5pt {}
				\item Worked on a small team to build an Autonomous Ground Vehicle (AGV) prototype using the NVIDIA Isaac ecosystem and ROS2.
				\item Trained custom stabilization model using IMU data to improve the AGV's stability on uneven terrain and to optimize speed.
				\item Integrated various sensors, including LiDAR and cameras, to enhance the AGV's environmental awareness, obstacle avoidance, and object detection capabilities.
			\end{itemize}			
		\end{itemize}

		Hyster-Yale Materials Handling - \textit{Global Tools Team} \hfill \textit{Fairview, OR}
		\begin{itemize} \itemsep -5pt {}
			\item Developed and maintained C$^\sharp$ applications used for internal tools that interface with Hyster and Yale forklifts.
			\item Worked directly with cross-functional teams to gather requirements, design features, and implement solutions that improved tool efficiency and user experience.
			\item Implemented automated testing and continuous integration processes to enhance software reliability and reduce deployment times.
		\end{itemize}

		\textbf{Intern} \hfill Sept 2022 - May 2023 \\
		Seasalt.AI \hfill \textit{Remote}
		\begin{itemize} \itemsep -5pt {} 
			\item Helped build Vietnamese and Indonesian Language Models used for Automated Speech Recognition.
			\item Used Kaldi and K2 to build Acoustic Models.
			\item Used Time Delay Neural Network to retrain our Vietnamese model and minimize Word Error Rate.
		\end{itemize}
	
		\textbf{Assistant Manager} \hfill Oct 2013 - Jan 2025 \\
		Music World \hfill \textit{Vancouver, WA}
		\begin{itemize} \itemsep -5pt {} 
			\item Managed small team of $\sim$4.
			\item Regularly trained new hires and mentored associates. 
			\item Created training materials and documentation to share knowledge and speed up on-boarding.
		\end{itemize}
	\end{rSection} 

	%----------------------------------------------------------------------------------------
	%	Projects
	%----------------------------------------------------------------------------------------
	
	% \begin{rSection}{PROJECTS}

		% Website creation
		% Resume repo with actions
		%\textbf{Using SPI with GPIO Expander:} Working with a Raspberry Pi Nano and a GPIO expander, I wrote C code to communicate between the two devices using bit-banging. Device specifics can be found in my GitHub repository. You can see the code and project report write up \href{https://github.com/gloghry/CS466_sub/tree/working/lab4}{here}.

	% \end{rSection} 


	%----------------------------------------------------------------------------------------
	%	EDUCATION
	%----------------------------------------------------------------------------------------
	\begin{rSection}{Education}
		{\bf Bachelor of Computer Science} \hfill {Fall 2023} \\
		\medskip{\emph{Washington State University} (WSU) \hfill{\emph{Vancouver, WA}}}\\
		Relevant Coursework: Embedded Systems, Operating Systems, Assembly, Systems Programming, Software Design, Algorithms, Digital Forensics, Object Oriented Design.
	\end{rSection}

	%----------------------------------------------------------------------------------------
	%	REFERENCES
	%----------------------------------------------------------------------------------------
	\vfill
	\begin{center}
		% \par{\scriptsize{References supplied upon request}}
	\end{center}


\end{document}


